A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-24 1_intro.tex
lil rewording
redo accuracy and width figures

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Distributed_accuracy.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Red signifies overfill and blue underfill.
}
\label{intro_wedge}
\end{figure}

>>>>

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
}
\label{intro_wedge}
\end{figure}

### 2019-08-24 6_validation.tex
redo accuracy and width figures

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Naive}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
blue areas in the top images signify underfill regions,
red areas overfill,
orange areas triply extruded areas (double overfill).
The bottom visualizes the bead widths at each location at \SI{90}{\percent} width.
Cold colors are narrower than the nozzle size $w_\text{pref}$ and warm colors are wider than the nozzle size.
}
\label{visualized_accuracy}
\end{figure*}

>>>>

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Naive}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}
